Illustrating splines using the Worcester Heart Attack Study

### 2024-06-13 text/14/axis.Rmd

---
title: "Some simple examples of manipulating the axes in a graph"
author: "Steve Simon"
source: "http://www.pmean.com/axis.html"
date: "2014-01-01"
category: Blog post
tags: Sample size
output: html_document
---

>>>>

---
title: "Some simple examples of manipulating the axes in a graph"
author: "Steve Simon"
source: "http://www.pmean.com/axis.html"
date: "2014-01-01"
category: Blog post
tags:
- Sample size justification
output: html_document
page_update: partial
---

### 2024-06-13 text/14/qqplot.Rmd

---
title: "The qqplot"
author: "Steve Simon"
source: "http://www.pmean.com/qqplot.html"
date: "2014-01-01"
category: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
output: html_document
---

@@

You can use the housing data set to illustrate the use of the normal probability prlot.
```{r read-and-display-data}
fn <- "http://www.pmean.com/00files/housing.txt"
al <- read.table(file=fn,header=TRUE)
head(al)
tail(al)
```

@@

Figure 1. Normal probabilty plot for house prices.

>>>>

---
title: "The qqplot"
author: "Steve Simon"
source: "http://www.pmean.com/qqplot.html"
date: "2014-01-01"
category: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
output: html_document
page_update: partial
---

@@

You can use the housing data set to illustrate the use of the normal probability plot.

```{r read-and-display-data}
fn <- "http://www.pmean.com/00files/housing.txt"
al <- read.table(file=fn,header=TRUE)
head(al)
tail(al)
```

@@

Figure 1. Normal probability plot for house prices.

### 2024-06-13 text/14/wavelets.Rmd

---
title: "An introduction to wavelets using R"
author: "Steve Simon"
source: "http://www.pmean.com/wavelets.html"
date: "2014-01-01"
category: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
output: html_document
---

>>>>

---
title: "An introduction to wavelets using R"
author: "Steve Simon"
source: "http://www.pmean.com/wavelets.html"
date: "2014-01-01"
category: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
output: html_document
page_update: partial
---

### 2024-06-13 text/22/r-creatures.Rmd
Fixed two typos in r-creatures

---
title: "Different creatures in the R zoo"
author: "Steve Simon"
source: new
date: "2022-04-14"
category: 
- Blog post
tags:
- R programming
output: html_document
---

@@

You can (and probably should) use names for each element of your list. This makes it easier to pick out pieces of list.

@@

The programming team working on the tidyverse has developed an alternative to the data frame called a tibble. You use the `tibble` function to create a tibble. But first you have to load the tidyverse packages (or just the tibble package by itself)

>>>>

---
title: "Different creatures in the R zoo"
author: "Steve Simon"
source: new
date: "2022-04-14"
category: 
- Blog post
tags:
- R software
output: html_document
---

@@

You can (and probably should) use names for each element of your list. This makes it easier to pick out pieces of list. Either of the first two statements will add names to a list.

@@

The programming team working on the tidyverse has developed an alternative to the data frame called a tibble. You use the `tibble` function to create a tibble. But first you have to load the tidyverse packages (or just the tidyr package by itself)

### 2024-06-13 text/23/non-standard-evaluation.Rmd

---
title: "Non-standard evaluation inside functions and loops"
source: "New"
date: "2023-04-04"
categories:
- Blog post
tags:
- R programming
output: html_document
---

>>>>

---
title: "Non-standard evaluation inside functions and loops"
source: "New"
date: "2023-04-04"
categories:
- Blog post
tags:
- R software
output: html_document
---

### 2024-06-13 text/24/diamond-spline.Rmd

---
title: Illustrating splines using the diamond pricing dataset
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Nonlinear regression
- R programming
output: html_document
---

>>>>

---
title: Illustrating splines using the diamond pricing dataset
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Nonlinear regression
- R programming
output: html_document
page_update: complete
---

### 2024-06-13 text/24/survival-spline.Rmd

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(broom)
library(pspline)
library(readr)
library(rms)
library(tidyverse)
library(yaml)
f0 <- "https://raw.githubusercontent.com/pmean/datasets/master/"
f1 <- "whas100-data-dictionary.yaml"
dd <- read_yaml(paste0(f0, f1))
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(broom)
library(pspline)
library(readr)
library(rms)
library(tidyverse)
library(yaml)
f0 <- "https://raw.githubusercontent.com/pmean/datasets/master/"
f1 <- "whas100.yaml"
dd <- read_yaml(paste0(f0, f1))
```
